---
title: "First Knit"
author: "Mirian Maldonado"
date: "August 19, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  


I am sitting in the back of the class on the firft row. I normally like to sit towards the front of the class.
The computer number I am currently sitting at is number 31.
I don't really care for seat re-assignments.
Yes, I have worked in teams in a class setting.
###my answer     
  
   
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

I don't have any nicknames, so I like be called by my fist name.
###my answer     
  
   
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?


I would like to change careers into something I am more passionate about. 
Science has always been a favorite subject of mine and can't wait to take these.
I aspire to get a nursing degree from AVC.
###my answer     
  
   
 




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?


Yes, I like to travel and have been to Ecuador, Peru, Mexico, Jamaica, Spain, France and Italy.
No, I have never been in the military.
###my answer     
  
   
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?


I would love to attain an A in this class to increase my GPA level. The higher my GPA the more likely I am to be accepted into the nursing program.
###my answer     
  
   
 





##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?


I rate myself about a 7, I know a mouse from a keyboard but not quite the computer geek.
I have a MAC at home. 
Yes, I have internet access at home. 
I have my own transportation and have no issues getting to class.
I graduated from Pacoima Skill Center (independent study) in 1998.
Yes, I am currently working at a Mortgage Company.
###my answer   
  
   
  




